Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-05 manuscript/manuscript.Rmd
Add to manuscript

Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by @Ark2019, who refer to their model as TabNet. 
In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data modelling using deep neural networks. 
This is done by structuring the neural networks to emulate a key aspect of decision tree modelling, which is the efficient selection of relevant covariates
for the model task. Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$. 
The covariates are multiplied by the attention scores to down-weight less relevant features for the prediction problem. Other less important details of the Tabnwet
model are given in @Ark2019.

@@

### Model 6: Neural Network with Unidimensional Embeddings

### Model 7: Neural Network with Unidimensional Embeddings

Can we get some lift by adding attention layers? TabNet model Transformer model

Description of tabnet, talk about how it's related to embeddings, show some plots 
like \@ref(fig:masks) etc.

```{r masks, echo = FALSE, fig.cap = "blahblah", out.width = "100%", fig.align = "center"}
knitr::include_graphics("images/masks.png")
```

>>>>

Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by @Ark2019, who refer to their model as TabNet. 
In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data modelling using deep neural networks. 
This is done by structuring the neural networks to emulate a key aspect of decision tree modelling, which is the efficient selection of relevant covariates
for the model task. Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$. 
The covariates are multiplied by the attention scores to down-weight less relevant features for the prediction problem. Other less important details of the TabNet
model are given in @Ark2019.

@@

### Model 6: TabTransformer
Whereas Model 5 makes a simple modification to the structure of Model 4, the TabTransformer model is slightly more complex. With respect to
similarities between Model 5 and 6, both use embeddings with a standard 8 dimensions for each categorical covariate. In terms of differences,
Model 6 uses a Transformer layer in place of self-attention and a positional encoding of a single dimension, i.e. $d_col = 1$. The TabTransformer
architecture is shown in Figure Figure \@ref(fig:nn-3).

```{r nn-3, echo = FALSE, fig.cap = "Architecture of Model 6.", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/tabt.pdf")
```

### Model 7: TabNet
The final model we consider in this subsection is the TabNet architecture. The structure of the model is quite similar to Model 6, except 
that a more specialized form of self-attention is used to select the most important covariates for the modelling problem.

## Explaining Attention Based models

## Results
